Pool Model

### 2025-08-21 pool_model.tex
Corresc mistakes

This so-called preparation to the exponential growth includes synthesys of the needed compounds, initiation of the transciption~\cite{rolfe_lag_2012} and poorly studied physiological and regulatory mechanisms~\cite{monod_growth_1949}.

@@

At the same time dying cells release the nutritions for survivors to continue growing.

@@

According to the works of Jacques Monod, in the system where all needed nutritients are in excess except for one the total growth is linear to the concentration of this limiting nutritient~\cite{monod_growth_1949}.

@@

Using release of the extracellular signalling molecules (autoinducers) it is possible to synchronize the gene expression of the whole group~\cite{ng_bacterial_2009}.

@@

This survival strategy can appear in response to different external stresses, e.g., nutritient deficiency, temperature stress or extreme fluctuations of environment parameters.

@@

As a result, species $A$ was able to suppress species $B$ consuming the larger amount of nutritient and reaching larger bacterial count at the end.

@@

However, in reality spatial effects can play a significant role for population survival forcing some species develop competitive mechanisms such as cell adhesion to surfaces in the areas rich with nutritients~\cite{htuson_bacteriasurface_2013}.

@@

%     \item \cite{farrell_mechanically_2013}: 2D modeling using Newtonian dynamics and only mechanical interactions + nutritient diffusion.

@@

%     \item \cite{farrell_mechanically_2013}: Showed the influence of mechanic interactions between bacteria in 2D system with bacteria consuming the nutritient.

@@

%     Exponential growth where diffusion of the nutritient does not play any role. Sublinear growth where growth is limited by nutritient diffusion.

@@

%     Can use citation when talk about general processes we are accounting as growth, uptake of nutritient, production of inhibitor, e.g.,:

@@

It has to be noted that the resource pool is normalized by its initial value, ie $R^* = R/R_0$.
Moreover, the species $A$ is able to release a certain antimicrobial component $I$ that shows inhibitory effect on species 2 (amensalism).

>>>>

This so-called preparation to the exponential growth includes synthesis of the needed compounds, initiation of the transcription~\cite{rolfe_lag_2012} and poorly studied physiological and regulatory mechanisms~\cite{monod_growth_1949}.

@@

At the same time dying cells release the nutrients for survivors to continue growing.

@@

According to the works of Jacques Monod, in the system where all needed nutrients are in excess except for one the total growth is linear to the concentration of this limiting nutrient~\cite{monod_growth_1949}.

@@

Using release of the extracellular signalling molecules (autoinducer molecules) it is possible to synchronize the gene expression of the whole group~\cite{ng_bacterial_2009}.

@@

This survival strategy can appear in response to different external stresses, e.g., nutrient deficiency, temperature stress or extreme fluctuations of environment parameters.

@@

As a result, species $A$ was able to suppress species $B$ consuming the larger amount of nutrient and reaching larger bacterial count at the end.

@@

However, in reality spatial effects can play a significant role for population survival forcing some species develop competitive mechanisms such as cell adhesion to surfaces in the areas rich with nutrients~\cite{htuson_bacteriasurface_2013}.

@@

%     \item \cite{farrell_mechanically_2013}: 2D modeling using Newtonian dynamics and only mechanical interactions + nutrient diffusion.

@@

%     \item \cite{farrell_mechanically_2013}: Showed the influence of mechanic interactions between bacteria in 2D system with bacteria consuming the nutrient.

@@

%     Exponential growth where diffusion of the nutrient does not play any role. Sublinear growth where growth is limited by nutrient diffusion.

@@

%     Can use citation when talk about general processes we are accounting as growth, uptake of nutrient, production of inhibitor, e.g.,:

@@

It has to be noted that the resource pool is normalized by its initial value, i. e., $R^* = R/R_0$.
Moreover, the species $A$ is able to release a certain antimicrobial component $I$ that shows inhibitory effect on species 2 with any harmful effect on itself (amensalism).
